Stimuli Selection

### 2025-01-27 study2/experiment/stimuli_selection/selection.qmd
updated stimuli selection
now only 25 images of opposite-sex couples (rather than 30)

write.csv(selection, "stimuli_data.csv", row.names=FALSE)
knitr::kable(selection)
```

```{r}
#| code-fold: true
json <- selection |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()

>>>>

# Sum the arousal scores 
selection <- selection |>
  mutate(total_arousal = selection$Hetero_Men_Arousal + selection$Hetero_Women_Arousal,
         total_valence = selection$Hetero_Men_Valence + selection$Hetero_Women_Valence)

# arrange by the 25 highest scores of arousal and calculate the lowest arousal score
selection |>
  filter(Category == "Opposite-sex Couple") |>
  arrange(desc(total_arousal)) |>
  head(25) |>
  summarize(min_arousal = min(total_arousal)) # 8.8

#check how many images have a score of 8.8 and the ID of the one with the lowest valance
remove_image <- selection |> 
  filter(total_arousal == 8.8) |> # 3 
  filter(total_valence == min(total_valence)) |> 
  select(ID)

# last selection 
last_selection <- selection |>
  filter(!(Category == "Opposite-sex Couple" & total_arousal < 8.8)) |>
  filter(!(ID %in% remove_image))

write.csv(last_selection, "stimuli_data.csv", row.names=FALSE)
knitr::kable(selection)
```

```{r}
#| code-fold: true
json <- last_selection |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()
